---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# openlpgc

The goal of openlpgc is to provide an R interface in order to extract data from Las Palmas de Gran Canaria City Council [open data site](http://datosabiertos.laspalmasgc.es/). This package uses the [CKAN API](https://docs.ckan.org/en/2.8/contents.html) and is powered by the [ckanr](https://github.com/ropensci/ckanr) package.

This package is fully inspirated by the [`opendataes`](https://github.com/rOpenSpain/opendataes) package. 

## Installation

You can install the released version of `openlpgc` from Github with:

``` r
# install.packages("remotes")
remotes::install_github("openlpgc")
```

## Example

`openlpgc` has three main functions: 

* `lpgc_categories`: Search for available datasets for each category
* `lpgc_search`: Search datasets by keyword
* `lpgc_load`: Load the dataset (specified by its id)

Let's show two examples in order to illustrate what it's been stated above.

### Loading data after keyword search

Let's search all datasets that are related to environment ("medio ambiente", in Spanish). We are supposed to use the `lpgc_search` function for this:

```{r example}
library(openlpgc)
lpgc_search("medio ambiente")
```

Once we have the result, we just need to select the ID we want to load and pass it into `lpgc_load`:

```{r example load}
our_id <- lpgc_search("medio ambiente")$id[[1]]
lpgc_load(id = our_id)
```


`lpgc_load` **always** returns a list with two slots: the first one contains a metadata tibble with information extracted from the site and the second slot is filled with the data, if it was possible to read them.

### Loading data after keyword search

